---
title: "CDS"
author: "Jakob Mørup"
date: "9/21/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


1) Use R to figure out how many elements in the vector below are greater than 2.

```{r}
rooms <- c(1, 2, 1, 3, 1, NA, 3, 1, 3, 2, 1, NA, 1, 8, 3, 1, 4, NA, 1, 3, 1, 2, 1, 7, 1, NA)

sum(rooms>2, na.rm =TRUE)

```


2) What type of data is in the 'rooms' vector?

```{r}
class(rooms)

```


3) What is the result of running the median() function on the above 'rooms' vector?

```{r}
median(rooms)
```


4) Submit the following image to Github: Inside your R Project (.Rproj), install the 'tidyverse' package and use the download.file() and read_csv() function to read the SAFI_clean.csv dataset into your R project as 'interviews' digital object (see instructions in https://datacarpentry.org/r-socialsci/setup.html and 'Starting with Data' section). Take a screenshot of your RStudio interface showing

a) the line of code you used to create the object,

b) the 'interviews' object in the Environment, and

c) the file structure of your R project in the bottom right "Files" pane.

Save the screenshot as an image and put it in your AUID_lastname_firstname repository inside our Github organisation (github.com/Digital-Methods-HASS) or equivalent. Place here the URL leading to the screenshot in your repository.

```{r}
#install.packages("tidyverse") #commented out as I already have this package installed.

interviews <- read.csv("data/SAFI_clean.csv")

```

